Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-04-16 draft_report.qmd
Incorporated cardiac rehab data to project

::: {.callout-note icon="false"}
## Cardiac rehabilitation metrics

Cardiac rehabilitation metrics will be added once they become available from NACR (expected before 31/3/24)
:::

@@

-   All 4 tertiary prevention metrics follow the same pattern of activity rates with the highest rates being in the least diverse cluster (cluster 1), followed by clusters 2 and then cluster 5 (the most diverse) and cluster 3. Cluster 4 has the lowest activity rates.
:::

@@

|  Cluster  | Number of vaccinations | CHD synthetic prevalence | Rate (No. of vaccinations / CHD synthetic prevalence) | Global rate | Change in number of vaccinations to match global rate |
|:----------:|-----------:|-----------:|:----------:|:----------:|:----------:|
|           |                    *n* |                      *d* |                        *r=n/d*                        | *gr=𝚺n/𝚺d*  |                     *(gr-r) x d*                      |
|     1     |              3,356,002 |                1,228,453 |                         2.73                          |    1.92     |                      -1,001,284                       |
|     2     |              2,638,698 |                1,124,040 |                         2.35                          |    1.92     |                       -484,121                        |
|     3     |              1,862,430 |                1,181,796 |                         1.58                          |    1.92     |                        402,855                        |
|     4     |                476,616 |                  571,049 |                         0.83                          |    1.92     |                        617,979                        |
|     5     |                332,728 |                  415,950 |                         0.80                          |    1.92     |                        464,571                        |
| **Total** |          **8,666,474** |            **4,521,288** |                         1.92                          |             |                         **0**                         |

>>>>

@@

-   All the tertiary prevention metrics, except waiting time for elective PCI/CABG, follow broadly the same pattern of activity rates with the highest rates being in the least diverse cluster (cluster 1), followed by cluster 2 and then clusters 5 (the most diverse) and 3. Cluster 4 has the lowest activity rates.
-   The rate for waiting time for elective PCI/CABG is greatest in the most diverse cluster (cluster 5) and lowest in cluster 4, although overall there is little variation between the clusters.
:::

@@

|  Cluster  | Number of vaccinations | CHD synthetic prevalence | Rate (No. of vaccinations / CHD synthetic prevalence) | Global rate | Change in number of vaccinations to match global rate |
|:---------:|----------:|----------:|:------------:|:---------:|:------------:|
|           |                    *n* |                      *d* |                        *r=n/d*                        | *gr=𝚺n/𝚺d*  |                     *(gr-r) x d*                      |
|     1     |              3,356,002 |                1,228,453 |                         2.73                          |    1.92     |                      -1,001,284                       |
|     2     |              2,638,698 |                1,124,040 |                         2.35                          |    1.92     |                       -484,121                        |
|     3     |              1,862,430 |                1,181,796 |                         1.58                          |    1.92     |                        402,855                        |
|     4     |                476,616 |                  571,049 |                         0.83                          |    1.92     |                        617,979                        |
|     5     |                332,728 |                  415,950 |                         0.80                          |    1.92     |                        464,571                        |
| **Total** |          **8,666,474** |            **4,521,288** |                         1.92                          |             |                         **0**                         |
